A Tool for Visualizing Patterns of Spreadsheet Function Combinations \\ \large The Protracted and Generally Unpleasant Death of Justin A. Middleton\\ A Methodological Obituary

### 2016-03-12 doc/paper.tex
Linear repeating gradients! Resolves #14

\begin{document}
\title{The Protracted and Generally Unpleasant Death\\ of Justin A. Middleton\\ \large A Methodological Obituary}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Finding information on how people use built-in Excel functions individually is easy; how they're used together is not. With no analysis of functions in conjunction, a dearth on information about how end users construct more sophisticated programs within spreadsheets restricts current research. I've developed a visualization tool, informed by existing spreadsheet corpora, which offers insight into the patterns of how formulas comprise several functions in practice. Even in its initial state, the tool illustrates how some people think that have 27 arguments in a single SUM function is, for whatever reason, a good idea.
\end{abstract}

>>>>

\begin{document}
\title{A Tool for Visualizing Patterns of Spreadsheet Function Combinations \\ \large The Protracted and Generally Unpleasant Death of Justin A. Middleton\\ A Methodological Obituary}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Spreadsheet environments often come equipped with a plethora of functions to manipulate and calculate data, but it can be difficult to understand how end-users employ these functions in practice. Without this knowledge, both researchers and practitioners lack information about how end users construct sophisticated programs from these basic elements. We developed a tool that visualizes patterns of how functions are combined into formulae within Excel spreadsheets. Using the Enron spreadsheet dataset as an example, this paper shows how the tool can display both common and anomalous formulas and their respective contexts in an actual workbook.
\end{abstract}
